---
title: "CAL Demo"
author: "Ellen Jiang"
date: "`r Sys.Date()`"
output: html_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This is a demo vignette for the package **ChutesAndLadders**. 

We will define and create a game board for an old-fashioned game *Chutes and Ladders*, demonstrate a solo player game, perform simulation, visualize the results, and answer some statistical questions.

The following lines of code runs the entire example

```{r}
#ChutesAndLadders Monte Carlo simulation
rm(list=ls())
set.seed(5)
library(ChutesAndLadders)
```

# Part 1: Board representation

```{r}
#Create a single `board` where you store the features of the game board.
h <- 10
w <- 10
ladder <- list(c(1, 38), c(4,14), c(9,31), c(21,42), c(28,84), c(36,44), c(51,67),c(71,91), c(80,100))
chute <- list(c(98,78), c(95,75), c(93,73), c(87,24), c(64,60), c(62,19), c(56,53), c(49,11), c(47,26), c(16,6))
board <- define_board(h, w, ladder, chute)
```

# Part 2: Plot of Game board

```{r}
# par() should help the plot be more visible.
par(mar = c(0, 0, 0, 0))
# show_board(board)
show_board(board)
```

# Part 3: Verbose output of one single player game

```{r}
set.seed(5)
play_solo(board, verbose = TRUE)
```

# Part 4: Monte Carlo Simulation

```{r}
sim <- simulate_board(board, n=10000)
newturns <- sim[[1]]
newladder <- sim[[2]]
newchute <- sim[[3]]

#The distribution of number of total turns
hist(newturns, breaks = 50, main = paste("Histogram of the turns" ))

#Frequency of ladders
barplot(colSums(newladder)/sum(newladder),
        main = "Relative Frequency of Ladders",
        xlab = "Ladder Number",
        ylab = "relative frequency")

#Frequency of chutes
barplot(colSums(newchute)/sum(newchute),
        main = "Relative Frequency of Chutes",
        names.arg = seq(length(board[[4]]),1,-1),
        xlab = "Chute Number",
        ylab = "relative frequency")
```

# Part 5: Results Interpretation

The above simulation can help answer a lot of questions. Let us take a look.

- Find the minimum number of turns. How many times out of 10,000 did a game finish with the minimum number of turns?
```{r}
min(newturns) #minimum nubmer of turns
length(which(newturns == 7)) # number of times out of 10,000 that min_turn occurs
```

- Find the maximum number of turns.
```{r}
max(newturns)
```

- What is the median number of turns?
```{r}
median(newturns)
```

- What is the mean number of turns?
```{r}
mean(newturns)
```

- What proportion of games take 100 or more turns to complete?
```{r}
length(which(newturns >= 100))/sum(newturns)
```

- What proportion of games take 10 or fewer turns to complete?
```{r}
length(which(newturns <= 10))/sum(newturns)
```

- What proportion of games utilize ladder 9 (the shortcut to win on space 80)?
```{r}
length(which(newladder[,9] != 0))/10000
```

